SST_patterns

### 2019-08-28 SST_patterns.Rmd
updated

@@

MUR_pixels <- unique_pixels(df = MUR)
# SACTN_pixels <- unique_pixels(df = SACTN)
OISST_pixels <- unique_pixels(df = OISST)
CMC_pixels <- unique_pixels(df = CMC)

@@

CMC_temp_PN <- match_func(df = CMC, xy = CMC_match_PN)
CMC_temp_LB <- match_func(df = CMC, xy = CMC_match_LB)
CMC_temp_SB <- match_func(df = CMC, xy = CMC_match_SB)
CMC_temp_SP <- match_func(df = CMC, xy = CMC_match_SP)
CMC_temp_HB <- match_func(df = CMC, xy = CMC_match_HB)
```

>>>>

CMC <- CMC %>% 
  select(site, lon, lat, temp.y)

@@

MUR_pixels <- unique_pixels(df = MUR)
# SACTN_pixels <- unique_pixels(df = SACTN)
OISST_pixels <- unique_pixels(df = OISST)
OISST_pixels <- OISST_pixels[-c(2),]

CMC_pixels <- unique_pixels(df = CMC)

@@

CMC_temp_PN <- match_func(df = CMC, xy = CMC_match_PN)
CMC_temp_LB <- match_func(df = CMC, xy = CMC_match_LB)
CMC_temp_SB <- match_func(df = CMC, xy = CMC_match_SB)
CMC_temp_SP <- match_func(df = CMC, xy = CMC_match_SP)
CMC_temp_HB <- match_func(df = CMC, xy = CMC_match_HB)

OISST_temp_PN <- match_func(df = OISST, xy = OISST_match_PN)
OISST_temp_LB <- match_func(df = OISST, xy = OISST_match_LB)
OISST_temp_SB <- match_func(df = OISST, xy = OISST_match_SB)
OISST_temp_SP <- match_func(df = OISST, xy = OISST_match_SP)
OISST_temp_HB <- match_func(df = OISST, xy = OISST_match_HB)
```
